\pkg{depmixS4} : An \proglang{R}-package for hidden Markov models

### 2010-02-22 papers/jss/dpx4Rev.tex
Sweave related files.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/depmix@357 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\SweaveOpts{echo=FALSE}
\usepackage{a4wide}

@@

\begin{document}

@@

A simple example that will run in any S engine: The integers from 1 to
10 are
<<print=TRUE>>=
1:10
<<results=hide>>=
print(1:20)
@ % the above is just to ensure that 2 code chunks can follow each other

We can also emulate a simple calculator:
<<echo=TRUE,print=TRUE>>=
1 + 1
1 + pi
sin(pi/2)
@

@@

<<>>=
library(stats)
x <- rnorm(20)
print(x)
print(t1 <- t.test(x))
@
Note that we can easily integrate some numbers into standard text: The
third element of vector \texttt{x} is \Sexpr{x[3]}, the
$p$-value of the test is \Sexpr{format.pval(t1$p.value)}. % $

@@

\SweaveOpts{echo=true}

% the following code is R-specific, as data(iris) will not run in Splus. 
% Hence, we mark it as R code. 
<<engine=R>>=
data(iris)
summary(iris)
@ %def

\begin{figure}[htbp]
  \begin{center}
<<fig=TRUE>>=
library(graphics)
pairs(iris)
@
    \caption{Pairs plot of the iris data.}
  \end{center}
\end{figure}

\begin{figure}[htbp]
  \begin{center}
<<fig=true>>=
boxplot(Sepal.Length~Species, data=iris)
@
    \caption{Boxplot of sepal length grouped by species.}
  \end{center}
\end{figure}

% R is not S-PLUS, hence this chunk will be ignored:
<<engine=S4>>=
function.that.comes.only.with.Splus(x)
@

>>>>

\usepackage{a4wide}

@@

\usepackage{Sweave}
\begin{document}

@@

A simple example that will run in any S engine: The integers from 1 to
10 are
\begin{Schunk}
\begin{Soutput}
 [1]  1  2  3  4  5  6  7  8  9 10
\end{Soutput}
\end{Schunk}

We can also emulate a simple calculator:
\begin{Schunk}
\begin{Sinput}
> 1 + 1
\end{Sinput}
\begin{Soutput}
[1] 2
\end{Soutput}
\begin{Sinput}
> 1 + pi
\end{Sinput}
\begin{Soutput}
[1] 4.141593
\end{Soutput}
\begin{Sinput}
> sin(pi/2)
\end{Sinput}
\begin{Soutput}
[1] 1
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Soutput}
 [1]  0.36039435 -1.83775608  1.04278935 -1.07035396 -0.82150164 -0.32257866
 [7]  0.97533933 -0.97446747  1.25840051 -1.01986278  1.15659229 -0.71535551
[13]  0.76128983  0.35511419  0.30919687 -1.45434289 -0.09874472 -0.13624640
[19] -1.57319360  1.32749121
\end{Soutput}
\begin{Soutput}
	One Sample t-test

data:  x 
t = -0.5432, df = 19, p-value = 0.5933
alternative hypothesis: true mean is not equal to 0 
95 percent confidence interval:
 -0.6012708  0.3534912 
sample estimates:
 mean of x 
-0.1238898 
\end{Soutput}
\end{Schunk}
Note that we can easily integrate some numbers into standard text: The
third element of vector \texttt{x} is 1.04278935363803, the
$p$-value of the test is 0.59332. % $

@@

% the following code is R-specific, as data(iris) will not run in Splus. 
% Hence, we mark it as R code. 
\begin{Schunk}
\begin{Sinput}
> data(iris)
> summary(iris)
\end{Sinput}
\begin{Soutput}
  Sepal.Length    Sepal.Width     Petal.Length    Petal.Width   
 Min.   :4.300   Min.   :2.000   Min.   :1.000   Min.   :0.100  
 1st Qu.:5.100   1st Qu.:2.800   1st Qu.:1.600   1st Qu.:0.300  
 Median :5.800   Median :3.000   Median :4.350   Median :1.300  
 Mean   :5.843   Mean   :3.057   Mean   :3.758   Mean   :1.199  
 3rd Qu.:6.400   3rd Qu.:3.300   3rd Qu.:5.100   3rd Qu.:1.800  
 Max.   :7.900   Max.   :4.400   Max.   :6.900   Max.   :2.500  
       Species  
 setosa    :50  
 versicolor:50  
 virginica :50  
\end{Soutput}
\end{Schunk}

\begin{figure}[htbp]
  \begin{center}
\begin{Schunk}
\begin{Sinput}
> library(graphics)
> pairs(iris)
\end{Sinput}
\end{Schunk}
\includegraphics{dpx4Rev-006}
    \caption{Pairs plot of the iris data.}
  \end{center}
\end{figure}

\begin{figure}[htbp]
  \begin{center}
\begin{Schunk}
\begin{Sinput}
> boxplot(Sepal.Length ~ Species, data = iris)
\end{Sinput}
\end{Schunk}
\includegraphics{dpx4Rev-007}
    \caption{Boxplot of sepal length grouped by species.}
  \end{center}
\end{figure}

% R is not S-PLUS, hence this chunk will be ignored:
